A portable, annotation-based, visual stepper for Common Lisp

### 2020-04-05 paper/paper.tex
* paper/paper.tex (subsection{Portability}): New subsection.

@@

We would like to thank Luís Oliveira and Michael Kirkland for early
comments and advice when discussing the stepper feature, as well as
Andrew Lawson for the encouragement to produce this work.

>>>>

\subsection{Portability}

The system as been described as ``portable'' or ``near-portable''.
Indeed, if a completely new conforming implementation of Common Lisp
were to spring into being, support for our stepper system would have
to deal with three potential sources of non-portability: (1) support
of the \texttt{AGNOSTIC-LIZARD} code-walking program, (2) differing
representations of constituent characters in readtables (for the
source-tracking reader described in section \ref{st-reader}), and (3)
support for ``gray streams''.  We defer the discussion of (1) to
\cite{agnostic-lizard}, noting that that system is built with
portability as its foremost requisite.  The ``shielding'' it offers is
useful e.g. in dealing with SBCL's implementation of
\texttt{CL:DEFMETHOD}, which itself produces a complicated
transformation of its body.  In (2), we note that the adjustments to
the read-table were needed only for SBCL's implementation, who doesn't
use a the macro-character function for constituents.  If the
hypothetical new implementation \emph{also} did so, it is plausible
that the current code would also support it.  Otherwise, if it were to
use a function (as the remaining implementations), it would probably
require no extra work as well.  Lastly, for (3), we think it
reasonable to expect support for ``gray streams'' in new
implementations, since it is a widely adopted extension, and required
by SLY/Emacs to begin with.

@@

We would like to thank Luís Oliveira and Michael Kirkland for early
comments and advice when discussing the stepper feature, as well as
Andrew Lawson for the encouragement to produce this work.  We also
offer thanks to the reviewers who provided very insightful comments.
